Model LF

### 2022-12-08 Power point test.Rmd
Commit

plot(((wage_ds_t_02b - wage_ds_t_bs2b) / wage_ds_t_bs2b)*100, col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage", ylim= c(0,4));
lines(((wage_ds_t_02 - wage_ds_t_bs2) / wage_ds_t_bs2)*100, col= "red")
grid()

plot(((wage_ds_02b - wage_ds_bs2b) / wage_ds_bs2b)*100, col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
lines(((wage_ds_02 - wage_ds_bs2) / wage_ds_bs2)*100, col= "red")
grid()

@@

plot(((pconk_ds_02b - pconk_ds_bs2b)), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
lines((pconk_ds_02 - pconk_ds_bs2), col= "red");
grid()

plot(((ik_02b - ik_bs2b)), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
lines((ik_02 - ik_bs2), col= "red");
grid()
```

@@

```{r}
plot((unemp_02b-unemp_bs2b)*1000, col= "black");
lines((unemp_02 - unemp_bs2)*1000, col= "red")
```

>>>>

```{r, fig.width=10, fig.height=5}
par(mfrow=c(1,2))

plot(((wage_ds_t_02b - wage_ds_t_bs2b) / wage_ds_t_bs2b)*100, col= "red", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage", ylim= c(0,4));
lines(((wage_ds_t_02 - wage_ds_t_bs2) / wage_ds_t_bs2)*100, col= "black");
legend("top",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

plot(((wage_ds_02b - wage_ds_bs2b) / wage_ds_bs2b)*100, col= "red", xlab= "Year", ylab= "% Change in wages", main= "Wages");
lines(((wage_ds_02 - wage_ds_bs2) / wage_ds_bs2)*100, col= "black")
legend("top",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

@@

```{r, fig.width=10, fig.height=10}
par(mfrow=c(2,2))

plot(((pconk_ds_02b - pconk_ds_bs2b)), col= "red", xlab= "Year", ylab= "Change in consumption", main= "Consumption");
lines((pconk_ds_02 - pconk_ds_bs2), col= "black");
legend("left",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

plot(((ik_02b - ik_bs2b)), col= "red", xlab= "Year", ylab= "Change in investments", main= "Investment");
lines((ik_02 - ik_bs2), col= "black");
legend("left",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

plot(((net_balance_02b - net_balance_bs2b)), col= "red", xlab= "Year", ylab= "Change in net-exports", main= "Net-exports");
lines((net_balance_02 - net_balance_bs2), col= "black");
legend("left",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

plot(((yk_ds_02b - yk_ds_bs2b)), col= "red", xlab= "Year", ylab= "Change in GDP", main= "GDP");
lines((yk_ds_02 - yk_ds_bs2), col= "black");
legend("left",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((unemp_02b-unemp_bs2b)*1000, col= "red", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Unemployment");
lines((unemp_02 - unemp_bs2)*1000, col= "black");
legend("left",legend=c("New version", "Old version"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```
